A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-26 paper/main.tex
revise intro regarding anno bottleneck

\section*{Introduction} Cognitive and psychiatric neuroimaging are moving
towards studying brain functions under conditions of real-life-like complexity
\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
\citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not,
lerner2011topographic} are increasingly utilized as so called ``naturalistic
stimuli''.

% data-driven methods
Naturalistic stimuli are usually not designed for research purposes but to
entertain their audience. Hence, their temporal is structure usually unknown due
to an ``annotation bottleneck'' \citep{aliko2020naturalistic}. Data-driven
methods like intersubject correlation (ISC)\citep{hasson2004intersubject} or
independent component analysis (ICA)\citep{bartels2004chronoarchitecture} are
often used to analyze corresponding fMRI data circumventing this bottleneck.
However, data-driven methods alone fall usually short of pinpointing their
results to specific stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to test
hypotheses on specific brain functions under more ecologically valid conditions,
to statistically control confounding stimulus features, and to explain not just
``how'' the brain is responding to a stimulus but also ``why''
\citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.

>>>>

\section*{Introduction}
% intro to intro
Cognitive and psychiatric neuroimaging are moving towards studying brain
functions under conditions of real-life-like complexity
\citep{sonkusare2019naturalistic, eickhoff2020towards}. Motion pictures
\citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not,
lerner2011topographic} are increasingly utilized as so called ``naturalistic
stimuli''.

% annotation bottleneck
Naturalistic stimuli are usually designed for commercial purposes and to
entertain their audience. Thus, the temporal structure of their feature space is
usually not explicitly known leading to an ``annotation bottleneck'' when used
for research purposes \citep{aliko2020naturalistic}.
% data-driven methods
Data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data circumventing this bottleneck. However, data-driven
methods alone fall usually short of pinpointing their results to specific
stimulus events \citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to test
hypotheses on specific brain functions under more ecologically valid conditions,
to statistically control confounding stimulus features, and to explain not just
``how'' the brain is responding to a stimulus but also ``why''
\citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
% combination of data-driven and model-driven approaches
Additionally, stimulus annotations can inform data-driven methods about a
stimulus' temporal dynamics, or model-driven and data-driven methods can be
combined to improve interpretability of results \citep{lahnakoski2012stimulus}.
